\vspace{-2cm} {\bf Online Appendix} \\ Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2019-08-01 paper/manuscript_psrmNote_OA.tex
added a (very long) footnote in the appendix on why we don't use the Internet Archive

To download the websites, we rely on the Unix command line tool \texttt{wget}. This program is used to download files from the Internet, and with the use of a recursive option, acts like a web crawler and scraper. This means that \texttt{wget} downloads HTML files, parses them and then follows the links contained therein. Then it follows those links and repeats the process until it has constructed a complete tree of the website (note that the program is instructed to stay on the same domain, i.e. it does not follow external links). This way, all the files that make up a website are downloaded. For some cities, whose websites make heavy use of JavaScript to serve content dynamically, such content is not reachable with our methodology and would require additional steps to obtain. For this paper, we ignore such sites and restricted our corpus to cities with at least three successfully downloaded pages.\footnote{There is a possibility that this leads to a small bias in selecting against cities with the resources to build more elaborate websites. However, given that our sample is generally more on the wealthy side, this, if anything, should lead to a more balanced sample.}

>>>>

To download the websites, we rely on the Unix command line tool \texttt{wget}.\footnote{An alternative source of web data which has attained some popularity within the digital humanities is the Internet Archive's Wayback machine (\url{https://archive.org/}), which preserves snapshots of websites over time. In theory, this would be very useful to projects such as ours, since it would allow us to measure the evolution of websites over time, in response to changes in city executives. However, the Wayback Machine suffers from some limitations that, in our eyes, inhibit its usefulness for scientific research in general, and our project in particular. First of all, the Internet Archive does not conduct all of its web crawling itself. Rather, third parties donate their crawling data to the Internet Archive. This means that the source of the data varies and the crawling process often remains opaque, which is a problem with respect to scientific transparency. Second, this also means that the crawling isn’t done in regular intervals unless the website in question is extremely prominent. Our research is focused on municipal websites, many of which are fairly obscure, preventing the Wayback Machine from being useful to us. For example, as of the time of writing, the website of Attica, IN, has only been crawled 25 times since the Wayback Machine's inception in 1996 (and in this case, all of these crawls are from 2014 on). By contrast, the website of New York City has been crawled over 7,000 times. Third, webcrawls are not instant and are not always done on an entire website at the same time. This means that for example, a website's frontpage might have been scraped one day, and its page on the city's mayor only a month later -- within the same crawl. Once again, this problem is exacerbated for small, less prominent websites. While we appreciate the Internet Archive's efforts to preserve snapshots of the web and recommend its API to practitioners who can work around the limitations outlined here, these problems preclude its usefulness for our purposes.} This program is used to download files from the Internet, and with the use of a recursive option, acts like a web crawler and scraper. This means that \texttt{wget} downloads HTML files, parses them and then follows the links contained therein. Then it follows those links and repeats the process until it has constructed a complete tree of the website (note that the program is instructed to stay on the same domain, i.e. it does not follow external links). This way, all the files that make up a website are downloaded. For some cities, whose websites make heavy use of JavaScript to serve content dynamically, such content is not reachable with our methodology and would require additional steps to obtain. For this paper, we ignore such sites and restricted our corpus to cities with at least three successfully downloaded pages.\footnote{There is a possibility that this leads to a small bias in selecting against cities with the resources to build more elaborate websites. However, given that our sample is generally more on the wealthy side, this, if anything, should lead to a more balanced sample.}
